\begin{center}
    \begin{tabularx}{\textwidth}{L R}
      {\large \textbf{INDUSTRY EXPERIENCE}} \\
        \textbf{Accenture} & \small \textbf{San Francisco, CA} \\
        \small \textbf{\textit{Technology Innovation Summer Associate Manager}} & \small May 2021--Aug 2021 \\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small Developed causal inferential frameworks applying the Targeted Learning methodology to leverage machine learning while maintaining robust statistical inference with applications to problems within supply chain management. Developed a simulation framework in Python to explore performance of various machine learning methods and provide insights to stakeholders.
        } \\
        \textbf{Verily Life Sciences --- Project Debug} & \small \textbf{South San Francisco, CA} \\
        \small \textbf{\textit{Data Science Intern}} & \small May 2019--Aug 2019 \\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small Developed statistical pipelines to provide realtime estimates of and inference around mosquito abatement techniques. Developed probabilistic spatial models of mosquito dispersal to inform and optimize adaptive mosquito release scheduling. Provided statistical guidance in developing experimental trial design.
        } \\
        \textbf{CytomX Therapeutics} & \small \textbf{South San Francisco, CA} \\
        \small \textbf{\textit{Database Developer}} & \small Oct 2013---Apr 2014 \\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small Developed SQL database to organize and make accessible in-vivo data generated by the Pharmacology group. Used VBA to develop an Excel/VBA based front-end to access and upload data for non-technical users. Carried out data analysis on publicly available gene expression data (The Cancer Genome Atlas) and built internal tools for data exploration and use by other members of company.
        } \\
        \small \textbf{\textit{Pharmacology/Bioinformatics Intern}} & \small May 2013--Aug 2013 \\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small Performed data analysis on publicly available gene expression data to identify potential targets for cancer therapeutics, then carried out cell cytotoxicity experiments at the bench to validate predictions. Carried out day-to-day tasks in the pharmacology group tasked with characterizing efficacy of novel cancer therapeutics, including maintaining cancerous mammalian cell lines and basic animal husbandry in a BSL 2 lab.
        } \\
    \end{tabularx}
\end{center}
