\begin{center}
    \begin{tabularx}{\textwidth}{L R}
        {\large \textbf{RESEARCH EXPERIENCE}} \\
        \textbf{University of California, Berkeley} & \small \textbf{Berkeley, CA} \\
        \small \textbf{Center for Targeted Machine Learning and Causal Inference } \\
        \small \textbf{\textit{Accenture Targeted Learning and Causal Inference Fellow}} & Jan 2020--Aug 2022\\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small Developed software for applying targeted learning and causal inference methodology with a focus on real industry use-cases, `big data' sets, and cluster trials. Developed novel approach to managing supply chain risk through state of the art survival analysis and machine learning.
        } \\
        \textbf{University of California, San Francisco} & \small \textbf{San Francisco, CA} \\
        \small \textbf{\textit{Graduate Student Researcher --- Principle Investigator: Bryan Greenhouse (Biohub)}} & Aug 2017--Current \\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small  Currently developing statistical models to infer underlying complexity of malaria infections using mixed genetic data and spatial models of population structure to infer origin of clinically detected infections. Providing support to lab members in developing statistical models for various bioinformatics pipelines.
        } \\
        \small \textbf{\textit{Staff Research Associate II | Lab Manager --- Greenhouse Lab/Malaria Elimination Initiative}} & Apr 2014--Aug 2017 \\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small Conducted large scale multiplex and nested PCR experiments to generate genetic data for malaria transmission mapping.  Developed data analysis pipeline and graphical user interface for high-throughput analysis of genetic data from malaria causing parasites. Developed applications for tracking clinical samples used in lab, and data visualization tools for analyzing transmission network based data. Carried out administrative duties of lab, managed other members of the lab, conducted PCR experiments on clinical samples, liaised with foreign clinical labs and provided technical support for protocols.
        } \\
    \end{tabularx}
\end{center}
