\begin{center}
    \begin{tabularx}{\textwidth}{L R}
        {\large \textbf{WORK/RESEARCH HISTORY}} \\
        \textbf{University of California, San Francisco} & \small \textbf{San Francisco, CA} \\
        \small \textbf{\textit{Graduate Student Researcher -- Principle Investigator: Bryan Greenhouse (Biohub)}} & Aug 2017 - Current\\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small  Currently developing statistical models to infer underlying complexity of malaria infections using mixed genetic data and spatial models of population structure to infer origin of clinically detected infections. Providing support to lab members in developing statistical models for various bioinformatics pipelines.
        } \\
        \small \textbf{\textit{Staff Research Associate II / Lab Manager -- Greenhouse Lab/Malaria Elimination Initiative}} & Apr 2014 - Aug 2017 \\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small Conducted large scale multiplex and nested PCR experiments to generate genetic data for malaria transmission mapping.  Developed data analysis pipeline and graphical user interface for high-throughput analysis of genetic data from malaria causing parasites. Developed applications for tracking clinical samples used in lab, and data visualization tools for analyzing transmission network based data. Carried out administrative duties of lab, managed other members of the lab, conducted PCR experiments on clinical samples, liaised with foreign clinical labs and provided technical support for protocols.
        } \\
        \textbf{CytomX Therapeutics} & \small \textbf{South San Francisco, CA} \\
        \small \textbf{\textit{Database Developer}} & \small Oct 2013 - Apr 2014 \\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small Developed SQL database to organize and make accessible in-vivo data generated by the Pharmacology group. Used VBA to develop an Excel/VBA based front-end to access and upload data for non-technical users. Carried out data analysis on publicly available gene expression data (The Cancer Genome Atlas) and built internal tools for data exploration and use by other members of company.
        } \\
        \small \textbf{\textit{Pharmacology/Bioinformatics Intern}} & \small May 2013 - Aug 2013 \\
        \multicolumn{2}{>{\hsize=\dimexpr2\hsize+2\tabcolsep+\arrayrulewidth\relax}X}{
            \small Performed data analysis on publicly available gene expression data to identify potential targets for cancer therapeutics, then carried out cell cytotoxicity experiments at the bench to validate predictions. Carried out day-to-day tasks in the pharmacology group tasked with characterizing efficacy of novel cancer therapeutics, including maintaining cancerous mammalian cell lines and basic animal husbandry in a BSL 2 lab.
        } \\
    \end{tabularx}
\end{center}
